### 2019-02-18 sections/introduction.tex
Fixes in 1.1

@@

Many applications these days are developed to support workflows in institutions and businesses.
Take for example expense declarations, order processing, and emergency management.
Some of these workflows occur on the boundary between organisations and customers,
like flight bookings or tax returns.
What they all have in common is,
that they need to interact with different people (end users, tax officers, customers, etc.)
and they use information from multiple sources (input forms, databases, sensors, etc.).

We call such interactive units of work based on information sources \emph{tasks}.
% Tasks stand for units of work in the real world, assigned to people.
Tasks model real world collaboration between users,
are driven by work they do,
and are assigned to some user.
Users could be people out in the field or sitting behind their desks,
as well as machines doing calculations or fetching data.

>>>>

\fixme{Common intro??}

@@

Many applications these days are developed to support workflows in institutions and businesses.
Take for example expense declarations, order processing, and emergency management.
Some of these workflows occur on the boundary between organisations and customers,
like flight bookings or tax returns.
What they all have in common is
that they need to interact with different people (end users, tax officers, customers, etc.)
and they use information from multiple sources (input forms, databases, sensors, etc.).

We call interactive units of work based on information sources \emph{tasks}.
% Tasks stand for units of work in the real world, assigned to people.
Tasks model real world collaboration between users,
are driven by work users do,
and are assigned to some user.
Users could be people out in the field or sitting behind their desks,
as well as machines doing calculations or fetching data.
